AUTHOR GUIDELINES FOR MLSP PROCEEDINGS MANUSCRIPTS

### 2017-05-31 paper/paper.tex
A plan for the paper

\maketitle
%
\begin{abstract}
The abstract should appear at the top of the left-hand column of text, about
0.5 inch (12 mm) below the title area and no more than 3.125 inches (80 mm) in
length.  Leave a 0.5 inch (12 mm) space between the end of the abstract and the
beginning of the main text.  The abstract should contain about 100 to 150
words, and should be identical to the abstract text submitted electronically
along with the paper cover sheet.  All manuscripts must be in English, printed
in black ink.
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

This is a good paper.

\section{CNN-CNN Autoencoder} 
The approximation $\hat X$ for a given spectrogram $X$ is computed as follows:

\begin{align}
	\hat H(k,t) =& ( \sum_{f,t'} X(f,t-t') F_e(f,t',k) ) \notag \\
	\hat X(f,t) =& \sum_k \sum_{t'} \hat H(k,t-t') F_d(f, t',k)
\end{align}

\section{RNN-CNN Autoencoder}
This is the same as CNN-CNN case, except the computation of the activations $H$. In the CNN encoder, each filter was of finite length. With RNN-CNN version, we are attempting to use an infinite length filter. The computation of $\hat H$ is as follows:

@@

@@

List and number all bibliographical references at the end of the paper.  The references can be numbered in alphabetic order or in order of appearance in the document.  When referring to them in the text, type the corresponding reference number in square brackets as shown at the end of this sentence \cite{C2}.

>>>>

\maketitle
%
\begin{abstract}
   In this paper we propose a convolutive and recurrent neural network based extensions to autoencoders for source separation. 
\end{abstract}
%
\begin{keywords}
One, two, three, four, five
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

Talk about what we are doing and why it is interesting. \\

Give some background.

\section{Autoencoders}

\subsection{Feed-forward Autoencoder} 
Define standard autoencoder. Provide a toy example to illustrate the shortcomings of this.

\subsection{CNN-CNN Autoencoder} 
The approximation $\hat X$ for a given spectrogram $X$ is computed as follows:

\begin{align}
	\hat H(k,t) =& \sigma_1\left ( \sum_{f,t'} X(f,t-t') F_e(f,t',k) \right ) \notag \\
	\hat X(f,t) =& \sigma_2 \left ( \sum_k \sum_{t'} \hat H(k,t-t') F_d(f, t',k) \right )
\end{align}

\subsection{Multilayer of CNN-CNN Autoencoder} 
This loses the interpretability, but maybe good for accuracy?

\subsection{RNN-CNN Autoencoder}

This is the same as CNN-CNN case, except the computation of the activations $H$. In the CNN encoder, each filter was of finite length. With RNN-CNN version, we are attempting to use an infinite length filter. The computation of $\hat H$ is as follows:

@@

Give a toy example which shows what this model can do that CNN-CNN can not.

\section{Experiments}

Try each model in a given $K$ range in speech-speech source separation task.

@@
